Assessing spatial correlations in pulsar timing arrays with the noise-marginalized optimal statistic

### 2017-08-02 manuscript/manuscript.tex
edits to introduction

Pulsar timing arrays (PTAs) are a conglomerate of pulsars with millisecond periods. 
Monitoring the ultra-regular periodic emission from these pulsars with radio telescopes 
enables us to probe the dynamics of the spacetime through which the pulses travel. 
PTAs are sensitive to gravitational waves (GWs) with frequencies of 
$10^{-9} - 10^{-7}\;\mathrm{Hz}$ \ki{citations needed}, 
which makes PTAs ideal complements to ground- and space-based GW detectors \sv{add citations}. 
\sv{something...} predict that the incoherent superposition of inspiraling SMBHBs form the dominant signal in this low-frequency regime \sv{add citations}.

>>>>

Low-frequency gravitational waves (GWs) with frequencies of 
$10^{-9} - 10^{-7} \; \mathrm{Hz}$ can be observed with pulsar timing arrays (PTAs) 
composed of millisecond pulsars (MSPs) \sv{citation}. 
By monitoring the ultra-regular periodic emission from these pulsars using radio telescopes, 
we can probe the dynamics of the spacetime through which the pulses travel. 
The dominant astrophysical source in this frequency range is an isotropic stochastic background 
made up of the incoherent superposition of GWs from inspiraling 
supermassive black hole binaries (SMBHBs) 
\citep{1995ApJ...446..543R, 2003ApJ...583..616J, 2003ApJ...590..691W}.
